Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-03-15 Manuscript/02-Method.Rmd
Clarify deviance

\subsection{Selecting Optimal Scale Values}
\label{sec:tune}
Our proposed models, BHAM, require two preset scale parameters ($s_0$, $s_1$). Hence, we need to find the optimal values for the scale parameters such that the model reaches its best prediction performance regarding a criteria of preference. This would be achieved by constructing a two-dimensional grid, consists of different pairs of ($s_0$, $s_1$) value. However, previous research suggested the value of slab scale $s_1$ have less impact on the final model and is recommended to be set as a generally large value, e.g. $s_1 = 1$, that provides no or weak shrinkage. [@Rockova2018] As a result, we focus on examining different values of spike scale $s_0$. Instead of the two-dimensional grid, we consider a sequence of $L$ decreasing values $\{s_0^l\}: 0 < s_0^1 < s_0^2 < \dots < s_0^L < s_1$. Increasing the spike scale $s_0$ tends to include more non-zero coefficients in the model. A measure of preference calculated with cross-validations (CV), e.g. deviance, area under the curve (AUC), mean squared error, can be used to facilitate the selection of a final model. The procedure is similar to the Lasso implemented in the widely used R package `glmnet`, which quickly fits Lasso models over a list of values of regularization parameters $\lambda$ , giving a sequence of models for users to choose from.

>>>>

\subsection{Selecting Optimal Scale Values}
\label{sec:tune}
Our proposed models, BHAM, require two preset scale parameters ($s_0$, $s_1$). Hence, we need to find the optimal values for the scale parameters such that the model reaches its best prediction performance regarding a criteria of preference. This would be achieved by constructing a two-dimensional grid, consists of different pairs of ($s_0$, $s_1$) value. However, previous research suggested the value of slab scale $s_1$ have less impact on the final model and is recommended to be set as a generally large value, e.g. $s_1 = 1$, that provides no or weak shrinkage. [@Rockova2018] As a result, we focus on examining different values of spike scale $s_0$. Instead of the two-dimensional grid, we consider a sequence of $L$ decreasing values $\{s_0^l\}: 0 < s_0^1 < s_0^2 < \dots < s_0^L < s_1$. Increasing the spike scale $s_0$ tends to include more non-zero coefficients in the model. A measure of preference calculated with cross-validations (CV), e.g. deviance \bg{(defined as model log-likelihood times -2, $-2\log f(\bs y|\bs{\hat\beta}, \hat\phi)$)}, area under the curve (AUC), mean squared error, can be used to facilitate the selection of a final model. The procedure is similar to the Lasso implemented in the widely used R package `glmnet`, which quickly fits Lasso models over a list of values of regularization parameters $\lambda$ , giving a sequence of models for users to choose from.
